\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\usepackage{hyperref} % Add hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\input{glyphtounicode}
\usepackage{xcolor}
\color{black} % Add this line to set the text color


%----------FONT OPTIONS----------
% serif
\usepackage{CormorantGaramond}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape A. Vivek Vardhan} \\ \vspace{1pt}
    \small 
    \href{tel:917989325150}{\raisebox{-0.1\height}\faPhone\ +91 7989325150} ~ 
    \href{mailto:vivekvardhan.akula@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{vivekvardhan.akula@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/vivek-vardhan369}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/vivek-vardhan369}} ~ 
    \href{https://github.com/vivekvardhan369}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/vivekvardhan369}} 
    \vspace{-6pt}
\end{center}




% \section{Summary of Qualifications}
% \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{
%       \item{
%         Results-driven Full Stack Developer with expertise in Django, Python, and JavaScript.
%       }
%       \item{
%         Proven track record of developing dynamic e-commerce platforms, improving user experiences, and implementing effective CI/CD pipelines.
%       }
%     }
%  \end{itemize}
%  \vspace{-16pt}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Bachelor of Technology in Information Technology}}{\textbf{2020-2023}}
      {\textbf{MLR Institute of Technology, Hyderabad, Telangana}}{\textbf{CGPA: 6.90/10}}
    \resumeSubheading
      {\textbf{Diploma in Electrical \& Electronics Engineering}}{\textbf{2017-2020}}
      {\textbf{Singareni Collieries Polytechnic, Telangana}}{\textbf{CGPA: 7.12/10}}
    \resumeSubheading
      {\textbf{SSC}}{\textbf{2016-2017}}
      {\textbf{Sachdeva School Of Excellence, Telangana}}{\textbf{CGPA: 8.7/10}}
  \resumeSubHeadingListEnd


\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{System Design and Architecture for Online Food Delivery Application} $|$ \emph{AWS, MongoDB, ReactJS, Node.js}}{September 2024}
          \resumeItemListStart
            \resumeItem{Conducted research and planning for a scalable, high-performance, and secure online food delivery system.}
            \resumeItem{Designed a scalable architecture for high availability and reliability.}
            \resumeItem{Proposed performance optimization strategies to\textbf{ reduce page load time by 30\%.}}
            \resumeItem{Developed a blueprint for real-time tracking and secure payment integration.}
            \resumeItem{Outlined data management and analytics tools for performance insights.}
            \resumeItem{Implemented robust security measures and seamless API integration.}
            \resumeItem{Utilized \textbf{Agile} and \textbf{Scrum methodologies} for project management and cross-functional collaboration.}
          \resumeItemListEnd
           \vspace{-16pt}
    \resumeSubHeadingListEnd





\resumeProjectHeading
    {\textbf{I-Shop (E-Commerce Platform)} $|$ \emph{React, Node.js, Express, MongoDB, Axios, Formik, Bootstrap}}{October 2024}
    \resumeItemListStart
        \resumeItem{Developed a high-performance, secure e-commerce platform with features like product search, multi-currency cart, and real-time inventory management.}
        \resumeItem{Implemented secure registration and login, \textbf{enhancing data security by 40\%.}}
        \resumeItem{Designed efficient product search and browsing, \textbf{reducing search time by 30\%.}}
        \resumeItem{Developed a multi-currency cart, increasing international \textbf{customer reach by 15\%.}}
        \resumeItem{Integrated diverse payment options and a shipping calculator for a seamless checkout experience.}
        \resumeItem{Built a comprehensive dashboard for product and order management, \textbf{improving administrative efficiency by 50\%.}}
        \resumeItem{Created secure\textbf{ RESTful APIs} for reliable data exchange with minimal response times.}
    \resumeItemListEnd
    \vspace{-16pt}


    
\resumeProjectHeading
    {\textbf{Video Management Platform} $|$ \emph{MERN (MongoDB, Express, React, Node.js), Redux Toolkit, Jest, Postman}}{August 2024}
    \resumeItemListStart
        \resumeItem{Developed a comprehensive video management system with features such as video upload, categorization, and analytics tracking.}
        \resumeItem{Designed and developed front-end and back-end components.}
        \resumeItem{Implemented state management with \textbf{Redux Toolkit} and conducted thorough testing.}
        \resumeItem{Optimized database queries and server-side logic.}
        \resumeItem{\textbf{GitHub Link:} \href{https://github.com/vivekvardhan369/Video-Management-Platform.git}{\underline{github.com/vivekvardhan369/Video-Management-Platform.git}}}
    \resumeItemListEnd
    \vspace{-16pt}



    
\resumeProjectHeading
    {\textbf{To-Do Application} $|$ \emph{MERN (MongoDB, Express, React, Node.js) with TypeScript, Redux Toolkit, Jest}}{July 2024}
    \resumeItemListStart
        \resumeItem{Built a feature-rich to-do application using the MERN stack with \textbf{TypeScript.}}
        \resumeItem{Developed modules for user registration and appointment scheduling.}
        \resumeItem{Led development of client-side and server-side features.}
        \resumeItem{Implemented comprehensive testing strategies and integrated \textbf{RESTful APIs.}}
        \resumeItem{Implemented user authentication and authorization using \textbf{cookies} and \textbf{JWT}, enhancing application security.}
        \resumeItem{\textbf{GitHub Link:} \href{https://github.com/vivekvardhan369/To-do-Application.git}{\underline{github.com/vivekvardhan369/To-do-Application.git}}}
    \resumeItemListEnd
    \vspace{-16pt}




\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
      \item{
        \textbf{Languages}{: C, C++, JavaScript (ES6+), TypeScript} \\
        \textbf{Frameworks/Libraries}{: React, Redux Toolkit, Node.js, Express, MongoDB, MySQL} \\
        \textbf{Tools}{: Git, Webpack, Babel, ESLint, Postman} \\
        \textbf{Testing}{: Jest, React Testing Library} \\
        \textbf{Others}{: RESTful APIs, Agile Methodologies, CI/CD, AWS} \\
      }
    }
 \end{itemize}
 \vspace{-16pt}



\section{Courses and Certificates}
    \resumeSubHeadingListStart
        \resumeSubheading
            {AI and Machine Learning Workshop}{E-CELL IIT Hyderabad and Techobytes Technologies}
            {Completion Date: February 2024}{}
        \resumeSubheading
            {Communication Masterclass}{Thinkschool}
            {Duration: (July 2023 - January 2024)}{}
        \resumeSubheading
            {Introduction to JavaScript Course}{Coding Ninjas}
            {Duration: (February 2021 - April 2021)}{}
        \resumeSubheading
            {Introduction to Git and GitHub}{Udemy}
            {Duration: (1 Month)}{}
    \resumeSubHeadingListEnd

    \section{Soft Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
      \item{\textbf{Communication Skills:} Effectively convey information both verbally and non-verbally. \textit{Demonstrated through completion of Thinkschool’s Communication Masterclass, which enhanced my engagement and clarity in team projects.}}
      
      \item{\textbf{Adaptability:} Quickly adjust to new changes and embrace learning opportunities. \textit{Demonstrated through completion of the AWS Cloud Practitioner course, facilitating effective implementation of scalable cloud solutions.}}
      
      \item{\textbf{Teamwork:} Collaborate effectively with diverse groups. \textit{Demonstrated through serving as Scrum Master for an online food delivery system project, leading to a 30\% reduction in page load time by resolving team impediments.}}
      
      \item{\textbf{Problem Solving:} Identify and implement effective solutions to challenges. \textit{Demonstrated through resolving a critical deadlock in a video management system project by optimizing database queries, ensuring timely completion and client satisfaction.}}
      
      \item{\textbf{Attention to Detail:} Ensure accuracy and thoroughness in work. \textit{Demonstrated through implementing comprehensive testing strategies and secure RESTful APIs in a to-do application, enhancing security and reliability with positive user feedback.}}
    }
\end{itemize}


\end{document}
